Exploring the Composition of Lithic Assemblages in Mesolithic South-Eastern Norway

### 2022-01-10 analysis/paper/paper.Rmd
Revisions and replies to reviewers

```{r, fig.height = 18, fig.cap = "Correspondence analysis using all original artefact categories. A) Row plot, B) Column plot.", fig.width = 10}
all_cats <- sites %>%
  # Make site names the rownames
  column_to_rownames(var = "no") %>% 
  # Deselect a few of the columns not be used
  select(-excavation_project, -excavated_m3, -dating_method)

@@

```{r, fig.height = 15, fig.cap = "Correspondence analysis collapsing artefact types irrespective of raw-material and including proportion of non-flint as its own variable. A) Row plot, B) Column plot."}

@@

```{r, fig.height = 15, fig.cap = "Same as above, only that here the proportion of non-flint is used as a supplementary column. The negligble difference between this CA and that above indicates that the flint/non-flint distinction is integrated in the different artefact types, and therefore that the effect of artefact types and raw material cannot be seperated. These plots thus hide important variability that is captured in the ones presented in the main text. A) Row plot, B) Column plot."}

>>>>

```{r supplementary1, fig.height = 18, fig.cap = "Correspondence analysis using all original artefact categories. A) Row plot, B) Column plot.", fig.width = 10}
all_cats <- sites %>%
  # Make site names the rownames
  column_to_rownames(var = "no") %>% 
  # Deselect a few of the columns not be used
  select(-excavation_project, -excavated_m3, -dating_method)

@@

```{r supplementary2, fig.height = 15, fig.cap = "Correspondence analysis collapsing artefact types irrespective of raw-material and including proportion of non-flint as its own variable. A) Row plot, B) Column plot."}

@@

```{r supplementary3, fig.height = 15, fig.cap = "Same as above, only that here the proportion of non-flint is used as a supplementary column. The negligble difference between this CA and that above indicates that the flint/non-flint distinction is integrated in the different artefact types, and therefore that the effect of artefact types and raw material cannot be seperated. These plots thus hide important variability that is captured in the ones presented in the main text. A) Row plot, B) Column plot."}
